Analytics Without Tuning Considered Harmful?

### 2015-08-09 tuningpredictor.tex
Updates from ShareLaTeX

@@

\begin{figure}[!b]
\includegraphics[width=3.5in,left]{np_10_90.eps}
\caption{Deltas in terms of F when using 10 and 90 as the population in DE. np=90 is better when the deltas are above zero.}\label{fig:deltas_np}
 \end{figure}

@@

\wei{added!} To justify that {\em np=10} is enough, we did another tuning study, 
where all the settings are the same as before but we chose {\em np=90} as recommended by Storn. 
The tuning performance of learners is evaluated
by F. To compare the results of {\em np=10} and {\em np=90}, we plot the delta in the performance as \fig{deltas}. In \fig{deltas_np}, 5 data sets are better but 4 data sets are worse when {\em np = 90} for WHERE. For CART and Random Forest, the numbers of better and worse data sets are both 4. The improvement for those better data sets is negligible to some extent but the deterioration is not. From this study, {\em np = 90}, which is recommended for WHERE and more than the number for CART and Random Forest, does not bring any significant improvement over {\em np=10}. Therefore, the searching space is very simple for tuning defect predictor, which makes tuning very simple.

>>>>

% \begin{figure}[!t]
% \begin{center}
% \includegraphics[width=1.5in]{svm_rbf.eps}\includegraphics[width=1.5in]{svm_sigmoid.eps}
%  \end{center}
% \caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
%  \end{figure}

@@

\begin{figure}[!b]
\begin{center}
\includegraphics[width=1.5in]{np_10_90_precision.eps}\includegraphics[width=1.5in]{np_10_90_f.eps}
 \end{center}
\caption{Deltas in terms of precision and F when using 10 and 90 as the population in DE. np=90 is better when the deltas are above zero.}\label{fig:deltas_np}
 \end{figure}

@@

\wei{added!I will run np=90,50,60 for WHERE, CART and RF,respectively} To justify that {\em np=10} is enough, we did another tuning study, 
where all the settings are the same as before but we chose {\em np=90} as recommended for tuning WHEREby Storn. 
To make the study simple, we also set {\em np=90} for CART. The tuning performance of learners is evaluated
by precision and F. To compare the results of {\em np=10} and {\em np=90}, we plot the delta in the performance as \fig{deltas}. As shown in \fig{deltas_np}, WHERE,CART has been improved in 7 datasets and deteriorated in 2. 5 data sets are better but 4 data sets are worse when {\em np = 90} for WHERE. For CART and Random Forest, the numbers of better and worse data sets are both 4. The improvement for those better data sets is negligible to some extent but the deterioration is not. From this study, {\em np = 90}, which is recommended for WHERE and more than the number for CART and Random Forest, does not bring any significant improvement over {\em np=10}. Therefore, the searching space is very simple for tuning defect predictor, which makes tuning very simple.
